Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-07-16 pirouette_supplement.tex

\new{
  We show in figures \ref{fig:example_6_taxa}, \ref{fig:example_12_taxa}, 
  \ref{fig:example_24_taxa}, \ref{fig:example_32_taxa} and 
  \ref{fig:example_40_taxa} what are the errors obtained when starting from 
  phylogenies with, respectively, 6, 12, 24, 32 and 40 taxa. Again we can see 
  that in each case errors tend to be greater in the true distribution than 
  in the twin distribution, similar to the result of the previous 
  subsection, subsection\ref{subsec:distribution}.
  In addition to this, we cannot detect a clear trend between the number of 
  taxa of the original phylogeny and the extent of such discrepancy. 
  Due to long computational times we have been able to provide data only 
  for a limited amount of replicates. 
  We cannot exclude that a clearer trend could be observed increasing the 
  number of replicates.
}

>>>>

\new{
  We show in figures \ref{fig:example_6_taxa}, \ref{fig:example_12_taxa}, 
  \ref{fig:example_24_taxa}, \ref{fig:example_32_taxa} and 
  \ref{fig:example_40_taxa} what are the errors obtained when starting from 
  phylogenies with, respectively, 6, 12, 24, 32 and 40 taxa. Again we can see 
  that in each case errors tend to be greater in the true distribution than 
  in the twin distribution, similar to the result of the previous 
  subsection, subsection \ref{subsec:distribution}.
  In addition to this, we cannot detect a clear trend between the number of 
  taxa of the original phylogeny and the extent of such discrepancy. 
  Due to long computational times we have been able to provide data only 
  for a limited amount of replicates. 
  We cannot exclude that a clearer trend could be observed increasing the 
  number of replicates.
}
